Shades of Green

### 2023-09-25 docs/presentations/20230928-sehm_presentation.qmd
update interactive plots of bioeconomy trends

## Count of Bioeconomy Innovation
### [Yearly]{.text-royal-blue-800} and [5 Year MA]{.text-gray-600}
```{python}
# label: fig-bioeconomy_count
#
#

@@

## Share of Bioeconomy Innovation{.smaller}
### [Yearly]{.text-royal-blue-800} and [5 Year MA]{.text-gray-600} 
```{python}

>>>>

## Count of Bioeconomy Innovation
### [5 Year MA]{.text-royal-blue-800} and [Yearly]{.text-gray-600}
```{python}
# label: fig-bioeconomy_count
#
#

@@

## Share of Bioeconomy Innovation{.smaller}
### [5 Year MA]{.text-royal-blue-800} and [Yearly]{.text-gray-600}
```{python}
